Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-02 manuscripts/paper-1/main.tex
Results are done

    \textbf{Simulation Model Review Results}

    F13 - The input controls in the discrete event simulation module was not complete or aligned with the actual inputs that will be provided by another system.

@@

    F18 - Discrete event Simulation module does not support parallel execution of micro-operations.

    F19 - The interruption mechanism of the assembly line was not considered within the DES module.

    F20 - The number of micro-operations was hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.

    F21 - Edge cases were not considered in the DES module.

@@

>>>>

    \textbf{Discrete Event Simulation Model Review Results}

    F13 - The input controls in the simulation module was not complete or aligned with the actual inputs that will be provided by another system.

@@

    F18 - The simulation module does not support parallel execution of micro-operations.

    F19 - The interruption mechanism of the assembly line was not considered within the simulation module.

    F20 - The number of micro-operations was hard coded, consequently, the simulation module must be reprogrammed every time, when a new micro-operation is needed.

    F21 - Edge cases were not considered in the simulation module.

@@

    To evaluate the quality of the FELICE digital twin, identified issues mapped to one or more relevant quality attributes(Table \ref{tab:Mapping}).
    The assessment revealed that a significant portion of the identified issues
     was quickly attributed to specific quality attributes.  Specifically, 24\% of the issues were related to correctness, 
     which indicates an error between the real system and a digital twin system. 
     35\% of the issues were related to completeness, proving that some necessary or appropriate parts were missing. 
     8\% of the issues were related to fidelity, indicating a lack of detail. 
     5\% of the issues were related to efficiency, indicating poor performance or excessive resource usage. 
     Finally, 28\% of the issues were related to evolvability, indicating that the system was unresponsive to the environment 
     and was not flexible or scalable.
